Evaluating computational methods for modeling off-normal operation of gas centrifuge cascades

### 2019-11-20 abstract.tex
done for the night ?
Added model product-feed plot. Changes to abstract/motivation.

\begin{abstract}

This work compares and evaluates different computational approaches for modeling
off-normal operation of a gas centrifuge enrichment cascade.

The goal of this work focuses on developing the necessary understanding of
potential misuse of enrichment cascades, contributing to more effective
international safeguards designs and approaches.  While it is straightforward to
design a symmetric enrichment cascade under ideal conditions as a function of the
theoretical feed, product and tails assays, it is very difficult to find
reliable information about the behavior of a given cascade when the feed assay
does not match the design value. Several methods have been developed to assess
the behavior of an enrichment cascade in such circumstances. In addition to the
cut ($\theta$) those methods evaluate the feed to product, feed to tails and the
product to tails enrichment ratio, respectively, $\alpha$, $\beta$ and $\gamma$,
as a function of the cascade feed assay. As those four parameters depend on each
other, determining two of them fully defines the other.  The first approach
consists of fixing $\theta$ and $\alpha$ recomputing the corresponding assays at
each stages of the cascade. The second one maintains the ideal condition of the
cascade ($\alpha$ and $\beta$ fixed across the whole cascade), modifying
$\theta$ value at each stage accordingly. Both approaches have been implemented
into the Cyclus fuel cycle simulator\cite{cyclus, mbmore.2018}. The third fixes
$\theta$ and $\gamma$, using both $\alpha$ and $\beta$ at each stage as free
parameters. The third method has been investigated in \cite{walker.2017}.

Following a description of each method and an evaluation of differences between
each approach, this work compares the results produced by these methods within
scenarios involving misuse of symmetric enrichment cascades simulated using the dynamic
nuclear fuel cycle simulator, Cyclus.

>>>>

\begin{abstract}
\begin{itshape}
    This work compares and evaluates different computational approaches for modeling
off-normal operation of a gas centrifuge enrichment cascade.

The goal of this work focuses on developing the necessary understanding of
potential misuse of enrichment cascades, contributing to more effective
international safeguards designs and approaches.  While it is straightforward to
design a symmetric enrichment cascade under ideal conditions as a function of the
theoretical feed, product, and tails assays, it is very difficult to find
reliable information about the behavior of a given cascade when the feed assay
does not match the design value. Several methods have been developed to assess
the behavior of an enrichment cascade in such circumstances. In addition to the
cut ($\theta$) those methods evaluate the feed to product, feed to tails, and the
product to tails enrichment ratio, $\alpha$, $\beta$ and $\gamma$, respectively,
as a function of the cascade feed assay. As those four parameters depend on each
other, determining two of them fully defines the other.  The first approach
consists of fixing $\theta$ and $\alpha$ recomputing the corresponding assays at
each stages of the cascade. The second one maintains the ideal condition of the
cascade ($\alpha$ and $\beta$ fixed across the whole cascade), modifying
$\theta$ value at each stage accordingly. Both approaches have been implemented
into the Cyclus fuel cycle simulator\cite{cyclus, mbmore.2018}. The third fixes
$\theta$ and $\gamma$, using both $\alpha$ and $\beta$ at each stage as free
parameters. The third method has been investigated in \cite{walker.2017}.

Following a description of each method and an evaluation of differences between
each approach, this work compares the results produced by these methods within
scenarios involving misuse of symmetric enrichment cascades simulated using the dynamic
nuclear fuel cycle simulator, Cyclus.
\end{itshape}

### 2019-11-20 motivation.tex
Added model product-feed plot. Changes to abstract/motivation.

The present work investigates the performance of an enrichment cycle when chaining
gas enrichment cascades tuned for low enrich uranium production from natural
uranium. As literature on the mater is for obvious reason limited, three
behavior models have been implemented and used to evaluate the response of an
enrich cascade when fed with different assays than the design one. This work
also takes advantage of the Cyclus\cite{cyclus} fuel cycle capabilities to
evaluate the assay values at equilibrium.

>>>>

The present work investigates the performance ofs an enrichment cycle when chaining
gas enrichment cascades tuned for low enrich uranium production from natural
uranium to instead produce HEU. As literature on the mater is for obvious reason
limited, three behavior models have been implemented and used to evaluate the
response of an enrichment cascade when fed with different assays than designed one.
This work also takes advantage of the Cyclus\cite{cyclus} fuel cycle capabilities
to evaluate the assay values at equilibrium.

### 2019-11-20 theory.tex
Added model product-feed plot. Changes to abstract/motivation.

>>>>

These models inherently result in differing amounts of diminishing returns
as can be seen in Figure \ref{fig:model_comparison}. As the product assay
weight percent increases, the required increase in feed assay to achieve the
same rate of increase grows. This is particularly true for Models A and C
compared to Model B.

\begin{figure}[ht]
    \centering
    \includegraphics[scale=0.4]{ModelComparison}
    \caption{}
    \label{fig:model_comparison}
\end{figure}
